Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-17 writeup/gz_hubble_data.tex
Incorporated abstract changes by KLM. Closes #83.

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various \textit{Hubble Space Telescope} Legacy programs that
used the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
GOODS-S), with filters selected to probe the rest-frame optical emission from
galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go
down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of
$\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH
morphological data include measurements of both bulge- and disk-dominated
galaxies, details on spiral disk structure that relate to the Hubble type, as
well as clump identification and geometry. This paper also describes and
employs a novel method for calibrating morphological bias by using
artificially-redshifted galaxy images as a baseline. The GZH catalog contains
both raw and calibrated morphological vote fractions for $150,771$ galaxies,
providing a comprehensive data set suitable for large-scale studies of galaxy
evolution. 
% didn't the GOODS-N and GOODS-S second phases go deeper than 23.5 mag? am I misremembering? --BDS

\end{abstract}

>>>>

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various \textit{Hubble Space Telescope} Legacy programs
using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
GOODS-S), with filters that probe the rest-frame optical emission from galaxies
out to $z\sim1$. The galaxies selected for GZH classifications go down to
magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle
z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH
morphological data include measurements of both bulge- and disk-dominated
galaxies, details on spiral disk structure that relate to the Hubble type, bar
identification, and numerous measuremenst of clump identification and geometry.
This paper also describes a new method for calibrating morphological bias by
using artificially-redshifted galaxy images as a baseline. The GZH catalog
contains both raw and calibrated morphological vote fractions for
$150,771$~galaxies, providing the largest data set to date suitable for
large-scale studies of galaxy evolution out to $z\sim1$. 
\end{abstract}
